\section{Code of Conduct}

The \symp is a gathering of experts across diverse yet convergent
fields related to ocean science and engineering. The symposium will
value the diversity of views, expertise, opinions, backgrounds, and
experience of those attending and is committed to providing a safe,
productive and welcoming environment for all present. By its very
nature, the symposium is expected to be an effective forum to consider
and debate science-relevant viewpoints in an orderly, respectful, and
fair manner. This Code of Conduct is important to promoting diversity
of ideas, opinions and thought and creating an inclusive, supportive,
and collaborative environment for all participants.

\subsection{Expected Behavior}

\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]

\item Treat all participants with kindness, respect, and consideration,
  valuing a diversity of views and opinions (including those you may not
  share).

\item Communicate openly, with respect for other participants,
  critiquing ideas rather than individuals.

\item Refrain from demeaning, discriminatory, or harassing behavior and
  speech directed toward other participants. 

\item Be mindful of your surroundings and of your fellow
  participants. Alert the organizers if you notice unacceptable
  behaviour (see below), a dangerous situation, or someone in distress.  

\item Please use discretion, and by default, ask for clarification
  rather than assuming others’ points of view.

\item Respect the rules and policies of the meeting venue, hotels and
  the location of the event.

\end{itemize}

\subsection{Unacceptable Behavior}

\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
  
\item Harassment, intimidation, or discrimination in any
  form. Harassment includes speech or behavior that is not welcome or is
  personally offensive. Behavior that is acceptable to one person may
  not be acceptable to another, so use discretion to be certain respect
  is communicated. Harassment intended in a joking manner still
  constitutes unacceptable behavior.

\item Examples of unacceptable behavior include, but are not limited to:

  \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]  

  \item Physical or verbal abuse of any participant
  \item Unwelcome or offensive verbal comments or exclusionary behavior
  related to age, appearance or body size, employment or military
  status, ethnicity, gender identity and expression, individual
  lifestyle, marital status, national origin, physical or cognitive
  ability, political affiliation, sexual orientation, race, or religion

\item Inappropriate physical contact
  
\item Unwanted sexual attention
  
\item Use of sexual or discriminatory images in public spaces or in
  presentations 

\item Deliberate intimidation, stalking, or following
  
\item Harassing photography or recording, including taking photographs
  or recording of another individual’s oral presentation or poster
  without the explicit permission of that individual 
\item Sustained disruption of talks or other events
\item Bullying behavior
\item Retaliation for reporting unacceptable behavior
\end{itemize}
\end{itemize}

\subsection{Consequences}

\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]  

\item Anyone requested to stop unacceptable behaviour is expected to
  comply immediately.
  
\item The symposium organizers (or their designees) may take any
  immediate action they deem necessary and appropriate, including
  removal from the meeting or event without warning or compensation of
  any kind. 
\item The matter may be referred to the errant participant's employer

\end{itemize}

The organizers can be reached anytime during the event via the hotel and
also via email at: \emph{azores-symp22-org@googlegroups.com}.