\section{Requested  support}

The overall budget for the \symp include all expenses for the
participants to come to the event from within Europe. No registration
is being charged, with the belief that to get the most out of the
participants, who have substantial expertise and in most cases at the
peak of their careers, covering these modest expenses will be in the
interests of what results we want to achieve with this event. In
addition, in the light of the pandemic and its resultant isolation, we
believe having this event in-person will make the effort worthwhile.
We are therefore requesting ONR Global's support for the \symp for
non-US national travel and room and board as also additional costs
related to convening this event, as shown in Table
\ref{tab:nsf-budget}.

\begin{table}[!h]
  \footnotesize{
    \centering    
    \begin{tabular}{|p{3.0cm}|p{1.6cm}|p{10cm}|}
      \hline 
      \rowcolor{Gray}
      \bfseries Item& \bfseries Estimated Costs (US \$)&\bfseries Description\\
      \hline
      Travel & \$15,000 & \$1000 per participant X 15 participants
                          travel from European home institutions\\ 
      \hline
      Lodging& \$7500 & \$100 per night per participant X 15 X 5
                        nights on Terceira Island (see attached quote)\\
      \hline
      Equipment and facility rental &\$2000 & Conf. room rental + A/V
                                              rental charges X 5 days
                                              (see attached quote)\\
      \hline
      Miscellany& \$250 & Materials and supplies for posters and writing material,
                          nametags, markers\\
      \hline
      Publication costs& \$2500 & Peer-reviewed journal publication
                                  costs\\
      \hline
      Facilitation costs& \$12500 & Visual facilitation by Marsha
                                    Dunn, with fees and travel
                                    costs; travel budgeted at \$1000 (see attached quote)\\
      \hline
      \textbf{Total}& \$39,750&\\
      \hline        
  \end{tabular}
  \caption{Budget request to ONR Global for support for 15 non-US
    nationals at \sympe + facilitation by a US national (Dunn).}
  \label{tab:nsf-budget}
}
\end{table}

\paragraph{Budget justification} Our request is primarily to support
non-US nationals participation to/from their home institutions and
their lodging at the venue hotel in Terceira Island, Azores. Other
related items for which support is being requested are conference room
rental where the event will take place, and some ancillary expenses
related to audio/visual equipment. Publication costs associated with a
manuscript in a peer-reviewed journal is also being requested.

Visual facilitation (Dunn) and her fees and travel are included in the
budget. We believe having Dunn participate and provide facilitation in
the form of visualizing complex inter-disciplinary ideas will not only
make this event viable in securely understanding concepts discussed,
but aid conversation and networking. In addition, all her output will
be made available to all participants in digital form, to help with
publications and proposal writing.

Hotel costs and Dunn's budget quotes are attached at the end of this
proposal. Finally, some miscellaneous expenses related to carrying out
the poster session and nametags. ONR Global funds will not be used for
any other expenses.

\subsection{Current \& Pending from other US govt. sources}

NSF will be supporting the \symp with a grant of \$40,303. NOAA is
contributing \$12,000.

\subsection{Other Resources}

\fla (the Luso-American Development Foundation, Portugal) is providing
support for the 3 ESR's to the symposium. The Ocean Foundation is
providing \$7000 towards networking costs.
