\section{Requested  support}

The overall budget for the \symp include all expenses for the
participants. No
registration is being charged. We do so with the belief that to get
the most out of the participants, who have substantial expertise and
in most cases at the peak of their careers, covering these modest
expenses will be in the interests of what results we want to achieve
with this event. In addition, in the light of the pandemic and its
resultant isolation, we believe having this event in-person will make
the effort worthwhile.  We are therefore requesting ONR Global's
support for the \symp for non-US national travel and room and board as
also additional costs related to convening this event, as shown in
Table \ref{tab:budget}.

\begin{table}[!h]
  \footnotesize{
    \centering    
    \begin{tabular}{|p{3.5cm}|p{1.6cm}|p{10cm}|}
    \hline 
    \rowcolor{Gray}
    \bfseries Item& \bfseries Estimated Costs (US \$)&\bfseries Description\\
    \hline
      Travel (Europe)& \$15,000 & \$1000 per participant (15 from Europe) \\
    \hline
      Travel (US)& \$22,500 & \$1500 per participant (15 from the US) \\
    \hline
      Food& \$12,150 & \$50 for Dinner + \$30 lunch + \$10 Coffee
                       breaks all days X 30 X 4.5 days\\
    \hline
      Lodging& \$18,000 & \$120 per night per participant X 30 X 5 nights in Angra do Heroismo, Terceira Island\\
    \hline
      Hotel conference room &\$1,000 & \$200 per day rental charges X 5\\
    \hline
      Outdoor networking& \$1,500 & Hike/picnic and/or cruise\\
    \hline
      Posters/Name tags/misc& \$100 & Miscellany for posters and writing material\\
    \hline
    \textbf{Total}& \$70,250 &\\
    \hline        
  \end{tabular}
  \caption{Estimated costs for the \sympe. We expect 27 scholars and 3
    ESRs (to be competitively selected) spread across disciplines,
    geography and gender at the meeting.}
  \label{tab:budget}
}
\end{table}

\paragraph{Budget justification} Our request is primarily to support
non-US nationals participation to/from their home institutions and
their lodging at the venue hotel in Terceira Island, Azores. Other
related items for which support is being requested are conference room
rental where the event will take place, and some ancillary expenses
related to audio/visual equipment. Publication costs associated with a
manuscript in a peer-reviewed journal is also being requested. Visual
facilitation (Dunn) and her fees and travel are included in the
budget. Hotel costs and Dunn's budget quotes are attached at the end
of this proposal. Finally, some miscellaneous expenses related to
carrying out the poster session and nametags. ONR Global funds will
not be used for any other expenses.

\subsection{Current \& Pending from other US govt. sources}

NSF will be supporting the \symp with a grant of \$40,303.

\subsection{Other Resources}

\fla (the Luso-American Development Foundation, Portugal) is
interested in providing support for the 3 ESR's to the symposium. The
Ocean Foundation is expected to provide \$5000 towards networking
costs.
