\section{Purpose of the event}

The main aim of this symposium is to generate ideas for novel ways at
observing the world’s upper-ocean bio-geochemical and dynamics
processes, by getting together a group of high-level scientists across a
wide range of disciplines (science, technology and computational and
robotic intelligence).

The symposium will gather a small number of people that will hold a very
interactive discussion through an innovative format. Each attendee will
present their ideas and will be challenged by other attendees from
different disciplines, in order to enhance interdisciplinary discussions
and favour new ideas. We expect people to present speculative and
“far-out” yet grounded ideas/hypotheses/concepts which commingle with
inter-disciplinary concepts, processes and actions. This symposium is an
attempt to bring people together in meaningful debate and interaction
across disciplinary, geographic and cultural boundaries, and do so in an
immersive, safe and thoughtful environment, where reaching out can
provide research dividends.

In addition to generating new ideas on ocean observation and advancing
this field with the latest developments and cross-disciplinary ideas,
this symposium will also benefit the creation of new contacts among
attendees, which can translate to new project ideas and future
collaborations.

In order to hold a meaningful discussion, the attendance will be limited
to 30 persons, and will be on invitation only. As we are expecting
people to stay for the duration of the event (4 days) and invest time,
energy and ideas into it, we want to cover their travel and
accommodation expenses.
